Hydra Battles and Cie

### 2021-07-31 doc/part-hydras.tex
converting chapter 2 to alectryon (continued)

Thus, $ (1 + 11)$ rounds later, the \texttt{n1} field is equal to $2$, and 
\texttt{nh}   to $0$.

@@

\begin{Coqsrc}
Inductive one_step (i: nat) :
  nat -> nat -> nat -> nat -> nat -> nat -> Prop :=
| step1: forall a b c, one_step i a b (S c) a b c
| step2:  forall a b, one_step i a (S b) 0 a b (S i)
| step3: forall a, one_step i (S a) 0 0 a (S i) 0.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma step_battle : forall i a b c a' b' c', 
   one_step i a b c a' b' c' ->
   battle standard i (hyd  a b c)  (S i) (hyd a' b' c').
\end{Coqsrc}

@@

\begin{Coqsrc}
 Inductive steps : nat -> nat -> nat -> nat ->
                  nat -> nat -> nat -> nat -> Prop :=
| steps1 : forall i a b c a' b' c',
    one_step i a b c a' b' c' -> steps i a b c (S i) a' b' c'
| steps_S : forall i a b c j a' b' c' k a'' b'' c'',
    steps i a b c j a' b' c' ->
    steps j a' b' c' k a'' b'' c'' ->
    steps i a b c k  a'' b'' c''.

Definition reachable (i a b c : nat) : Prop :=
  steps 3 3 0 0 i a b c.
\end{Coqsrc}

@@

\begin{Coqsrc}
 Lemma steps_battle : forall i a b c j a' b' c', 
   steps i a b c j a' b' c' ->
   battle standard i (hyd  a b c)   j  (hyd a' b' c').
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LS : forall c a b i,  steps i a b (S c) (i + S c) a b 0.
Proof.
  induction c.
 -   intros;  replace (i + 1) with (S i).
     + repeat constructor.
     + ring.
 -  intros; eapply  steps_S.
   +   eleft;   apply rule1.
   +   replace (i + S (S c)) with (S i + S c) by ring;  apply IHc.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma doubleS_law : forall  a b i, steps i a (S b) 0 (doubleS i) a b 0.
Proof.
  intros;  eapply steps_S.
  +   eleft;   apply step2.
  +   unfold doubleS; replace (2 * S i) with (S i + S i) by ring; 
        apply LS.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma reachable_S  : forall i a b, reachable i a (S b) 0 ->
                                   reachable (doubleS i) a b 0.
Proof.
  intros; right with  (1 := H); apply doubleS_law.
Qed.
\end{Coqsrc}

From now on, the lemma \texttt{reachable\_S} allows us to watch larger steps of 
the battle.

\begin{Coqsrc}
 Lemma L4 : reachable 4 2 4 0.
Proof.
  left; constructor.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma L10 : reachable 10 2 3 0.
Proof.
  change 10 with (doubleS 4).
  apply reachable_S, L4.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma L22 : reachable 22 2 2 0.
Proof.
  change 22 with (doubleS 10).
  apply reachable_S, L10.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma L46 : reachable 46 2 1 0.
Proof.
  change 46 with (doubleS 22); apply  reachable_S, L22.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma L94 : reachable 94 2 0 0.
Proof.
  change 94 with (doubleS 46); apply reachable_S, L46.
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma L95 : reachable 95 1 95 0.
Proof.
  eapply steps_S.
  -  eexact L94.
  -  repeat constructor.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma Bigstep : forall b i a , reachable i a b 0 ->
                               reachable (iterate doubleS b i) a 0 0.
 Proof.
  induction b.
  -  trivial.
  -  intros;  simpl;   apply reachable_S in H.
     rewrite <- iterate_comm; now apply IHb.
 Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
 Definition M := (iterate doubleS 95 95).

Lemma L2_95 : reachable M 1 0 0.
Proof.
  apply Bigstep,  L95.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma L2_95_S : reachable (S M) 0 (S M) 0.
Proof.
  eright.
  - apply L2_95.
  -  left; constructor 3.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition N :=   iterate doubleS (S M) (S M).

Theorem   SuperbigStep : reachable N  0 0 0 .
Proof.
  apply Bigstep, L2_95_S.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma Almost_done :
  battle standard 3 (hyd 3 0 0) N (hyd 0 0 0).
Proof. 
  apply steps_battle, SuperbigStep.
Qed.

Theorem Done :
  battle standard 0 hinit N head.
Proof.
  eapply battle_trans.
  -   apply Almost_done.
  -  apply L_0_3.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition exp2 n := iterate (fun n => 2 * n) n 1.
\end{Coqsrc}
Using some facts (proven in 
\href{../theories/html/hydras.Hydra.BigBattle.html}{hydras.Hydra.BigBattle}),we get several  minorations.

\begin{Coqsrc}
Lemma minoration_0 : forall n,  2 * n <= doubleS n.

Lemma minoration_1 : forall n x, exp2 n * x <= iterate doubleS n x.

Lemma minoration_2 : exp2 95 * 95 <= M.

Lemma minoration_3 : exp2 (S M) * S M <= N.

Lemma minoration : exp2 (exp2 95 * 95) <= N.
\end{Coqsrc}

>>>>

Thus, $(1 + 11)$ rounds later, the \texttt{n1} field is equal to $2$, and 
\texttt{nh}   to $0$.

@@

\input{movies/snippets/BigBattle/oneStep}

@@

\input{movies/snippets/BigBattle/stepBattle}

@@

\input{movies/snippets/BigBattle/steps}

@@

\input{movies/snippets/BigBattle/stepsBattle}

@@

\input{movies/snippets/BigBattle/LS}

From now on, the lemma \texttt{reachable\_S} allows us to watch larger and larger steps of 
the battle.

\input{movies/snippets/BigBattle/L4}

\input{movies/snippets/BigBattle/L10To95}

@@

\input{movies/snippets/BigBattle/Bigstep}

@@

\input{movies/snippets/BigBattle/MDef}

@@

\input{movies/snippets/BigBattle/L295S}

@@

\input{movies/snippets/BigBattle/NDef}

@@

\input{movies/snippets/BigBattle/Done}

@@

\input{movies/snippets/Exp2/exp2Def}

Using a few facts (proven in 
\href{../theories/html/hydras.Hydra.BigBattle.html}{hydras.Hydra.BigBattle}),we get several  minorations.

\input{movies/snippets/BigBattle/minorationLemmas}
